---
title: "EDA Correlation"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

Correlation matrix is a  comprehensive overview of our feature space. 
It shows whether two features are connected so that one changes with a predictable trend if you change the other. The closer this coefficient is to zero the weaker is the correlation. Both 1 and -1 are the ideal cases of perfect correlation and anti-correlation.



1.Data load and preparation. For the purpose of this plot we will recode  categorical features as integers. 

```{r}
#
dataset <- read.csv('data/fdata_v1_trgencd.csv',stringsAsFactors = FALSE )
#spaces
dataset <- data.frame(lapply(dataset, trimws), stringsAsFactors = FALSE)

target <- 'hasclaim'
continuous <- c( 
 'modelscore',
 'external_length_in',
 'external_width_in',
 'external_height_in',
 'external_vehicleage',
 'vehicleage',
 'ratingvalue',
 'estimatedannualdistance',
 'odometerreading',
 'daysperweekdriven',
 'driverage',
 'havelicenseage',
 'mvrstatusage',
 'garageterritory',
 'vehnumber',
 'drivernumber',
 'viol_pointschargedterm',
 'acci_pointschargedterm',
 'viol_driverpointsnumbercountterm',
 'acci_driverpointsnumbercountterm',
 'viol_infractioncdcountterm',
 'acci_infractioncdcountterm',
 'viol_last_infractionage',
 'acci_last_infractionage',
 'viol_last_convictionage',
 'acci_last_convictionage',
 'external_engine',
 'enginesize',
 'enginehorsepower',
 'external_make_encd',
 'external_model_encd',
 'manufacturer_encd',
 'model_encd',
 'registrationstateprovcd_encd',
 'vehbodytypecd_encd',
 'performancecd_encd',
 'restraintcd_encd',
 'antitheftcd_encd',
 'enginecylinders_encd',
 'vehusecd_encd',
 'classcd_encd',
 'carpoolind_encd',
 'daylightrunninglightsind_encd',
 'passiveseatbeltind_encd',
 'programtypecd_encd',
 'driverstatuscd_encd',
 'licensedstateprovcd_encd',
 'relationshiptoinsuredcd_encd',
 'scholasticdiscountind_encd',
 'mvrstatus_encd',
 'maturedriverind_encd',
 'drivertrainingind_encd',
 'gooddriverind_encd',
 'accidentpreventioncourseind_encd',
 'persontypecd_encd',
 'gendercd_encd',
 'maritalstatuscd_encd',
 'occupationclasscd_encd')


dataset[continuous] <- sapply(dataset[continuous], as.numeric)
```

2. Libraries
```{r}
library(dplyr)
library(corrplot)

```

3. Correlation matrix

```{r}
dataset[continuous] %>%
  cor(use="complete.obs", method = "spearman") %>%
  corrplot(type="lower", tl.col = "black",  diag=FALSE)
```

In this kind of plot we want to look for the bright, large circles which immediately 
show the strong correlations (size and shading depends on the absolute values of the 
coefficients; colour depends on direction). Anything that you would have to squint to see is usually not worth seeing.

4. Let's reduce the set of features to most correlated and our plot will be easier to read and more informative.

```{r}
v_set <- c(
 'hasclaim',    
 'external_vehicleage',
 'vehicleage',
 'external_length_in',
 'external_width_in',
 'external_height_in',
 'external_engine',
 'enginesize',
 'enginehorsepower',
 'antitheftcd_encd',
 'enginecylinders_encd',
 'restraintcd_encd',
 'passiveseatbeltind_encd',
 'vehbodytypecd_encd',
 'manufacturer_encd',
 'model_encd',
 'external_make_encd',
 'external_model_encd'
 )
dataset[v_set] <- sapply(dataset[v_set], as.numeric)
dataset[v_set] %>%
  cor(use="complete.obs", method = "spearman") %>%
  corrplot(type="lower", tl.col = "black",  diag=FALSE)
```

```{r}
mvr_set <- c(
 'hasclaim',  
 'mvrstatusage',
 'mvrstatus_encd',
 'viol_pointschargedterm',
 'acci_pointschargedterm',
 'viol_driverpointsnumbercountterm',
 'acci_driverpointsnumbercountterm',
 'viol_infractioncdcountterm',
 'acci_infractioncdcountterm',
 'viol_last_infractionage',
 'acci_last_infractionage',
 'viol_last_convictionage',
 'acci_last_convictionage')
dataset[mvr_set] <- sapply(dataset[mvr_set], as.numeric)
dataset[mvr_set] %>%
  cor(use="complete.obs", method = "spearman") %>%
  corrplot(type="lower", tl.col = "black",  diag=FALSE)
```


```{r}
o_set <- c(
 'hasclaim',
 'estimatedannualdistance',
 'odometerreading',
 'daysperweekdriven',
 'driverage',
 'drivernumber',
 'vehusecd_encd',
 'classcd_encd',
 'carpoolind_encd',
 'daylightrunninglightsind_encd',
 'driverstatuscd_encd',
 'relationshiptoinsuredcd_encd',
 'scholasticdiscountind_encd',
 'drivertrainingind_encd',
 'gooddriverind_encd',
 'accidentpreventioncourseind_encd')
dataset[o_set] <- sapply(dataset[o_set], as.numeric)
dataset[o_set] %>%
  cor(use="complete.obs", method = "spearman") %>%
  corrplot(type="lower", tl.col = "black",  diag=FALSE)
```


Target (hasclaim) is not correlated with any feature. Some of the correlations are expected. Like  length_in, height_in and width_in with model and vehicle dimensions.

Accidentpreventioncourseind is a part of drivertraingind. And they are correlated with enginetype.